Use of management strategy evaluation to inform in fisheries management in a changing climate

### 2019-08-28 Poster_ICES.Rmd
Change 'Publication' label to 'Reviewed'; remove unused plots and tables that separated Pub and CC results; and driver data table

---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0.1
#ESSENTIALS
title: Use of management strategy evaluation to inform in fisheries management in a changing climate
author:
  - name: '**Jonathan W. Cummings**'
    affil: 1
    main: true
    orcid: '0000-0001-8028-5787'
    twitter: jonwcummings 
    email: 'jcummings@umassd.edu'
  - name: Amanda Hart
    affil: 1
    main: true
    orcid: '0000-0002-6449-9328'
    email: 'ahart2@umassd.edu'
  - name: Gavin Fay
    main: true
    affil: 1
    email: 'gfay@umassd.edu'
affiliation:
  - num: 1
    address: School for Marine Science and Technology, University of Massachusetts - Dartmouth 836 South Rodney French Blvd,New Bedford, MA, USA 02744
main_findings:
  - "Make **better posters** with RMarkdown + **posterdown**.
  Use of management strategy evaluation to inform in fisheries management in a changing climate"
logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logocenter_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
---
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html")
##### load libraries #####
library(tidyverse) # upgrade to base R
library(readxl) # read in excel files
library(shiny) # Shiny App
library(shinythemes) # web themes for Shiny
library(DT) # Data Table
library(purrr) # for loop alternative
library(ggmap) # map plotting
library(mapdata) # basemap generation
library(odbc) # database connection 
library(RMySQL) # MySQL scripting in R
library(DBI) # database interface

@@

# label MSEs articles by analysis for ploting
freq.data_pub<-mutate(freq.data_pub,Analysis="Publication")
freq.data_CC<-mutate(freq.data_CC,Analysis="Climate Change")
freq.data<-rbind(freq.data_pub,freq.data_CC)
part.data_pub<-mutate(part.data_pub,Analysis="Publication")
part.data_CC<-mutate(part.data_CC,Analysis="Climate Change")
part.data<-rbind(part.data_pub,part.data_CC) %>% 
  arrange(Stage, Percent) %>%
  mutate(order = row_number())
part.data$order<-c(1,2,3,3,4,4,5,6,7,8,6,9,10,8,9,11,12,10,13,12,13,14,14,15,16,17,18,19,20,16,17,18,20,21,22,23,24,25,21,23,26,25,26,27,27,28,29,30,31,29,32,30,33,32,33,34,35,36,37,38,39,39)

@@

# plot explicit documentation of steps or components of MSE processes
# Publication MSEs
Freq.plot_pub<-ggplot(freq.data_pub,aes(Explicit,Percent))+
    geom_col()+geom_vline(xintercept=3.5,linetype="dashed")+
    coord_flip()+scale_y_continuous(limits=c(0,100),expand = c(0,0))+xlab(NULL)+
    scale_x_discrete(
      limits=c("Adopted","Open Meetings","Roles","Decision","Tradeoffs",
               "Alternatives","Objectives","Problem","Process"),
      labels=c("Adopted","Open Meetings","Roles","Decision","Tradeoffs",
               "Alternatives","Objectives","Problem","Process"))

#Climate Change MSEs
Freq.plot_CC<-ggplot(freq.data_CC,aes(Explicit,Percent))+
  geom_col()+geom_vline(xintercept=3.5,linetype="dashed")+
  coord_flip()+scale_y_continuous(limits=c(0,100),expand = c(0,0))+xlab(NULL)+
  scale_x_discrete(
    limits=c("Adopted","Open Meetings","Roles","Decision","Tradeoffs",
             "Alternatives","Objectives","Problem","Process"),
    labels=c("Adopted","Open Meetings","Roles","Decision","Tradeoffs",
             "Alternatives","Objectives","Problem","Process"))

Freq.plot<-ggplot(freq.data,aes(Explicit,Percent,fill=Analysis))+
  geom_col(position="dodge")+geom_vline(xintercept=3.5,linetype="dashed")+
  coord_flip()+scale_fill_manual(values=c("#FF0033","#0000FF")) +
  scale_y_continuous(limits=c(0,100),expand = c(0,0))+xlab(NULL)+
  scale_x_discrete(
    limits=c("Adopted","Open Meetings","Roles","Decision","Tradeoffs",
             "Alternatives","Objectives","Problem","Process"),
    labels=c("Adopted","Open Meetings","Roles","Decision","Tradeoffs",
             "Alternatives","Objectives","Problem","Process")) +
  guides(fill = guide_legend(reverse=T)) + theme_bw()

Part.plot_pub<-ggplot(part.data_pub,aes(x=order,y=Percent)) +
    facet_wrap(~Stage,scale="free",ncol=2) + geom_col() +
    scale_x_continuous(breaks = part.data_pub$order,
      labels = part.data_pub$Participants)+
  scale_y_continuous(limits=c(0,100),expand = c(0,0)) +
    ylab("Percent")+coord_flip()

Part.plot_CC<-ggplot(part.data_CC,aes(x=order,y=Percent)) +
  facet_wrap(~Stage,scale="free",ncol=2) + geom_col() +
  scale_x_continuous(breaks = part.data_CC$order,
                     labels = part.data_CC$Participants)+
  scale_y_continuous(limits=c(0,100),expand = c(0,0)) +
  ylab("Percent")+coord_flip()

@@

as_tibble(summary.data_pub)
as_tibble(summary.data_CC)
```

@@

| MSE type | Count |
|:--:|:--:|
| Published | ### |
| Reviewed | 30 |
| Climate Change | 11 |

@@

Here you may have some figures to show off, bellow I have made a scatterplot with the infamous Iris dataset and I can even reference to the figure automatically like this, `Figure \@ref(fig:irisfigure)`, Figure \@ref(fig:irisfigure).

```{r, irisfigure, fig.cap='Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="80%"}
par(mar=c(2,2,0,1))
plot(x = iris$Sepal.Length, y = iris$Sepal.Width,
     col = iris$Species, pch = 19, xlab = "Sepal Length",
     ylab = "Sepal Width")
```

Maybe you want to show off some of that fancy code you spent so much time on to make that figure, well you can do that too! Just use the `echo=TRUE` option in the r code chunk options, Figure \@ref(fig:myprettycode)!

```{r myprettycode, echo=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=6, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

How about a neat table of data? See, Table \@ref(tab:iristable):

>>>>

---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0.1
#ESSENTIALS
author:
  - name: '**Jonathan W. Cummings**'
    affil: 1
    main: true
    orcid: '0000-0001-8028-5787'
    twitter: jonwcummings 
    email: 'jcummings@umassd.edu'
  - name: Amanda Hart
    affil: 1
    main: true
    orcid: '0000-0002-6449-9328'
    email: 'ahart2@umassd.edu'
  - name: Gavin Fay
    main: true
    affil: 1
    email: 'gfay@umassd.edu'
affiliation:
  - num: 1
    address: School for Marine Science and Technology, University of Massachusetts - Dartmouth 836 South Rodney French Blvd,New Bedford, MA, USA 02744
main_findings:
  - "Make **better posters** with RMarkdown + **posterdown**.
  Use of management strategy evaluation to inform in fisheries management in a changing climate"
logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logocenter_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
---
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html")
##### load libraries #####
library(tidyverse) # upgrade to base R
library(readxl) # read in excel files
library(shiny) # Shiny App
library(shinythemes) # web themes for Shiny
library(DT) # Data Table
library(purrr) # for loop alternative
library(ggmap) # map plotting
library(mapdata) # basemap generation
library(odbc) # database connection 
library(RMySQL) # MySQL scripting in R
library(DBI) # database interface
library(kableExtra) # extra formating of the tables

@@

# label MSEs articles by analysis for ploting
freq.data_pub<-mutate(freq.data_pub,Analysis="Reviewed")
freq.data_CC<-mutate(freq.data_CC,Analysis="Climate Change")
freq.data<-rbind(freq.data_pub,freq.data_CC)
part.data_pub<-mutate(part.data_pub,Analysis="Reviewed")
part.data_CC<-mutate(part.data_CC,Analysis="Climate Change")
part.data<-rbind(part.data_pub,part.data_CC) %>% 
  arrange(Stage, Percent) %>% 
  mutate(order = row_number())
part.data$order<-c(1,2,3,3,4,4,5,6,7,8,6,9,10,8,9,11,12,10,13,12,13,14,14,15,16,17,18,19,20,
                   16,17,18,20,21,22,23,24,25,21,23,26,25,26,27,27,28,29,30,31,29,32,30,33,
                   32,33,34,35,36,37,38,39,39)
drive.data_pub<-mutate(drive.data_pub,Analysis="Reviewed") %>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,Driver,Percent,Frequency)
drive.data_CC<-mutate(drive.data_CC,Analysis="Climate Change")%>% 
  mutate(Percent=round(Percent,0)) %>% 
  select(Analysis,Driver,Percent,Frequency)
drive.data<-rbind(drive.data_pub,drive.data_CC) %>% 
  select(Analysis,Driver,Percent,Frequency) %>% 
  arrange(desc(Percent),Driver)

@@

# plot explicit documentation of steps or components of MSE processes
# Reviewed MSEs
Freq.plot<-ggplot(freq.data,aes(Explicit,Percent,fill=Analysis))+
  geom_col(position="dodge")+geom_vline(xintercept=3.5,linetype="dashed")+
  geom_vline(xintercept=1.5,linetype="dashed")+
  coord_flip()+scale_fill_manual(values=c("#FF0033","#0000FF")) +
  scale_y_continuous(limits=c(0,100),expand = c(0,0))+xlab(NULL)+
  scale_x_discrete(
    limits=c("Adopted","Open Meetings","Roles","Decision","Tradeoffs",
             "Alternatives","Objectives","Problem","Process"),
    labels=c("Adopted","Open Meetings","Roles","Decision","Tradeoffs",
             "Alternatives","Objectives","Problem","Process")) +
  guides(fill = guide_legend(reverse=T)) + theme_bw() +
  theme(legend.position = c(0.875,0.085),legend.title = element_blank())

@@

as_tibble(summary.data_pub)
as_tibble(summary.data_CC)
```
---
title: Use of management strategy evaluation to inform in fisheries management in a changing climate
---

@@

| MSE type | Count |
|:--:|:--:|
| Published | ### |
| Reviewed Sample | 30 |
| Climate Change | 11 |

@@

Map of where reviewed MSEs and climate change focues MSEs occurred: Figure \@ref(fig:mapfigure).

```{r, mapfigure, fig.cap='Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="100%"}
MSE.map
```

Figure \@ref(fig:explicit)!

```{r explicit, fig.cap='Percentage of MSEs that included explicit documentation of these SDM process steps!', fig.height=6, out.width="100%"}
text1<-expression(paste("Absent or \nInexplicit"))
text2<-paste("Absent")
text3<-paste("Unknown")
Freq.plot + annotate("text", x = 5, y = 55, label = text1, size=25) + 
  annotate("text", x = 2.6, y = 50, label = text2, size=20) + 
  annotate("text", x = 1, y = 50, label = text3, size=12)
```

Figure \@ref(fig:participants)!

```{r participants, fig.cap='Who participated during these stages of the SDM process', fig.height=6, out.width="100%"}
Part.plot
```

The drivers modeled in the reviewed MSEs Table \@ref(tab:driversPub) and the climate change MSEs Table \@ref(tab:driversCC) [description of results].

```{r, drivers}
color_Pub <- which(drive.data$Analysis=='Reviewed')
color_CC <- which(drive.data$Analysis=='Climate Change')

drive.data %>% 
  kable(align = "c") %>%
  row_spec(color_CC, color = "#FF0033", background = "white") %>% 
  row_spec(color_Pub, color = "#0000FF", background = "white")

knitr::kable(
  as_tibble(drive.data), format = "html",
  caption = "Drivers modeled in management strategy evaluations",
  align = "c", escape = FALSE)
```
